---
title: "OSSL paper analysis"
output: 
  github_document:
    toc: true
    toc_depth: 4
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library("tidyverse")
mnt.dir <- "~/projects/mnt-ossl/"
```

## Overview

Analysis code fore generating outputs for the OSSL paper.

The workspace development is defined by:

- GitHub repository: [whrc/ossl-paper](https://github.com/whrc/ossl-paper)

## Descriptive analysis

Number of unique samples correctly imported into the OSSL per original source and spectra type.

```{r table1, echo=FALSE}
table1 <- read_csv("outputs/table1_source_and_spectra_count.csv", show_col_types = F) %>%
  replace_na(list(visnir = 0, mir = 0, nir = 0))

table1 %>%
  knitr::kable()
```

Number of available samples for selected soil properties per spectra type and database subset.

```{r table2, echo=FALSE}
table2 <- read_csv("outputs/table2_soil_properties_count.csv", show_col_types = F)

table2 %>%
  knitr::kable()
```

Performance from 10-fold cross-validation

```{r table4, echo=FALSE}
table4 <- read_csv("outputs/table4_10CV_performance.csv", show_col_types = F)

table4 %>%
  knitr::kable()
```
